Groth16 zk-SNARK Proof Verification on Freeton : Three Use Cases

### 2021-07-13 submission/submission.tex
minor changes in submission

The previous example is somewhat limited by the fact that Sudokus are easily solvable problems, either by hand or with a computer; they are not a realistic use case of \zksnarks{}\footnote{Although they hint at a possible use for \zksnarks{}: checking a result without implementing its full logic in Solidity may save precious storage and computations on the blockchain}.

@@

Project Euler is sort of a gentlemen's competition. For example, competitors are supposed to have found the answer using a program running at most in one minute, but no mechanism enforces this. Still, some protections are in place, partly to enforce the spirit of the competition, and partly because of past abuse. For instance, a captcha system prevents one from attempting many solutions in a row. We decided to emulate the latter mechanism. If we simply gave a proving key to try and find the actual solution to the problem, users might be tempted to try to build a proof using every single integer until it works\footnote{We have noticed that although generating a correct proof may take time, an incorrect input is usually rejected in less than one second.}. Hence, the value they must find is actually
\[ \textrm{SHA256}^{1\,000\,000}\left(problem\_number | solution | nonce\right)\]
where the exponent denotes repeated application of the $\textrm{SHA256}$ hashing function, and `|` denotes the concatenation of strings. Note that this does not protect against replay attacks, which is why we also included a form of authentication described in Section~\ref{section_pincode}. This repeated application takes about 20 seconds on our laptops, which seems enough to discourage brute-force by all but the most determined cheaters.

>>>>

The previous example is somewhat limited by the fact that Sudokus are easily solvable problems, either by hand or with a computer; they are not a realistic use case of \zksnarks{}\footnote{Although they hint at a possible use for \zksnarks{}: checking a result without implementing its full logic in Solidity may save precious storage and computations on the blockchain.}.

@@

Project Euler is a gentlemen's competition. For example, competitors
are supposed to have found the answer using a program running at most
in one minute, but no mechanism enforces this. Still, some protections
are in place, partly to enforce the spirit of the competition, and
partly because of past abuse. For instance, a captcha system prevents
one from attempting many solutions in a row. We decided to emulate the
latter mechanism. If we simply gave a proving key to try and find the
actual solution to the problem, users might be tempted to try to build
a proof using every single integer until it works\footnote{We have
  noticed that although generating a correct proof may take time, an
  incorrect input is usually rejected in less than one
  second.}. Hence, the value they must find is actually
\[ \textrm{SHA256}^{1\,000\,000}\left(problem\_number | solution | nonce\right)\]
where the exponent denotes repeated application of the $\textrm{SHA256}$ hashing function, and `|` denotes the concatenation of strings. Note that this does not protect against replay attacks, which is why we also included a form of authentication described in Section~\ref{section_pincode}. This repeated application takes about 20 seconds on our laptops, which seems enough to discourage brute-force by all but the most determined cheaters.
